### 2016-03-17 paper.tex
Add bibtex citation example
Add a ~100 word abstract draft

\documentclass[a4]{article}                                     
\usepackage{url,xspace,epsfig,etoolbox}
\usepackage{natbib}
\usepackage{fullpage}
\usepackage[font=bf]{caption}
\usepackage{mdwlist}

@@

% Abstract: 150 words or less, extra 0.5in left and right margin.
% Note that all text is justified.
%
\begin{adjustwidth}{0.5in}{0.5in}
  \textbf{Abstract:}
 Text goes here.
\end{adjustwidth}

@@

Content goes here

>>>>

\documentclass[a4paper]{article}                                     
\usepackage{url,xspace,epsfig,etoolbox}
\usepackage{natbib}
\usepackage{fullpage}
\usepackage[font=bf]{caption}
\usepackage{mdwlist}

@@

% Abstract: 150 words or less, extra 0.5in left and right margin.
% Note that all text is justified.
%
\begin{adjustwidth}{0.5in}{0.5in}
  \textbf{Abstract:} \textit{Player-narration games} are a promising
  genre for transformative games. This genre can be defined formal and
  dramatic characteristics, and we identify tabletop games that belong
  to the genre.  Adding technological components to the game affords
  new interaction modes as well as convenient digital distribution. We
  describe our team's pilot project at creating a technology-enhanced
  player-narration game to improve cultural empathy among players aged
  10--14.  This pilot project highlights several complications with
  this genre, including thematic, technical, and production
  challenges.  However, the pilot project justifies continued
  experimentation, development, and formal assessment within the
  genre.
\end{adjustwidth}

@@

Content goes here.
We might cite \citet{Koster2013}, but this example is really just a placeholder
so the bibtex portion of the build script succeeds.

\section{Acknowledgments}
\textit{The team, organizational, and community partner
  acknowledgments are hidden for blind review.}
